WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-04-21 lit/sec_2-lead.tex
Before copy back from Google docs

\hl{The concept of the \acrshort{lead} is a workflow orchestration for on-demand, real-time and dynamically adaptive systems called WOORDS.} The system is doing the workflow orchestration as given in each procedure. Those procedural rules are defined by the researcher and feed into the system. The system is trying to act immediately after the submission, and also it transmits the data, run the models and send back the put with a lower time delay as possible. \hl{According to the load and other requirements, the system will respond to those requirements automatically.}

>>>>

The concept of the \acrshort{lead} \hl{is a workflow orchestration for on-demand, real-time and dynamically adaptive systems called WOORDS.} The system is doing the workflow orchestration as given in each procedure. Those procedural rules are defined by the researcher and feed into the system. The system is trying to act immediately after the submission, and also it transmits the data, run the models and send back the put with a lower time delay as possible. \hl{According to the load and other requirements, the system will respond to those requirements automatically.}

### 2020-04-21 method/sec_3-microservice.tex
Before copy back from Google docs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice in the \acrshort{wdias}, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v4.pdf}
    \caption{\acrshort{wdias} architecture for handling requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}
The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules. As explained section \cref{subse:dumb_pipes}, each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is an adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with the In-Memory database to fast access as mentioned in \cref{subse:redis}.
The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias}, other microservice use it to handle data for fast access.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice in the \acrshort{wdias}, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v4.pdf}
    \caption{\acrshort{wdias} architecture for handling requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}
The left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and the right side shows the export modules. As explained \cref{subse:dumb_pipes}, each import microservice only does the specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is an adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with the In-Memory database to fast access as mentioned in \cref{subse:redis}.
The system generates a unique identifier for each timeseries, and throughout the \acrshort{wdias}, other microservice use it to handle data for fast access.
